Meta-analysis

### 2019-09-15 03_Preliminary_analysis.Rmd
Format Rmd

```{r PA_Libraries, include=FALSE}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
#source("./getPPD2.R")
```

@@

   1) Fungicide type
   2) Fungicide dose
   3) row spacing
   4) Host cultivars (probably is a covariate with season due to changing cultivars over time)
   5) Experiment location
   6) Final disease rating

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <-
   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
colnames(PM_MB_means)
PM_MB_means$Fungicide_application_1[as.character(PM_MB_means$Fungicide_application_1) == ""] <-
   NA
PM_MB_means$Fungicide_application_2[as.character(PM_MB_means$Fungicide_application_2) == ""] <-
   NA
PM_MB_means$Fungicide_application_3[as.character(PM_MB_means$Fungicide_application_3) == ""] <-
   NA
PM_MB_means$Fungicide_application_4[as.character(PM_MB_means$Fungicide_application_4) == ""] <-
   NA
PM_MB_means$Fungicide_application_5[as.character(PM_MB_means$Fungicide_application_5) == ""] <-
   NA
PM_MB_means$Fungicide_application_6[as.character(PM_MB_means$Fungicide_application_6) == ""] <-
   NA
PM_MB_means$Fungicide_application_7[as.character(PM_MB_means$Fungicide_application_7) == ""] <-
   NA

# Rewrite all variations of sulphur treatments as just sulphur
PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur" |
                         PM_MB_means$Fungicide == "Sulphur (SC)" |
                         PM_MB_means$Fungicide == "Sulphur (Ultra SC)" |
                         PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
```

>>>>

```{r PA_Libraries, include=FALSE}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
source("R/import_data.R")
#source("./getPPD2.R")
```

@@

   1) Fungicide type

   2) Fungicide dose

   3) Row spacing

   4) Host cultivars (probably is a covariate with season due to changing cultivars over time)

   5) Experiment location

   6) Final disease rating

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <- import_data()
colnames(PM_MB_means)
```
